Modeling Two-Dimensional Vesicle Hydrodynamics with Hydrophobic Attraction Potential Simulations

### 2021-08-10 doc/main_jfm.tex
updates

Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of vesicles 
under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
interfacial tension $\gamma=4.1$ pN nm from ~\cite{Ryham16}. We then be able to calculate the corresponding 
time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
$\kappa=8.51$ kT $\approx35$ pN nm.

@@

\begin{figure}
\begin{center}
\hspace{-1cm}
\includegraphics[height=2in]{ReducedArea.pdf}
\hspace{-1cm}
\includegraphics[height=2in]{ArcLength.pdf}
\hspace{-1cm}
\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) Reduced area transitions over time. (c) Excess length of the midplanes.
A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
A slower shear rate generates a faster convergence in the reduced area and smaller excess length. 
  }
    \label{figure4}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[width=0.5\textwidth]{parabolic.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=10000$.
  }
    \label{figure6}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2.4in]{N58_rupt_0.pdf}
\includegraphics[height=2.4in]{N58_rupt_200.pdf}
\\
\includegraphics[height=2.4in]{N58_rupt_400.pdf}
\includegraphics[height=2.4in]{N58_rupt_600.pdf}
  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$. Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)). (c)-(d) are the later states during the simulation.
  }
    \label{figure7}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=1.2in]{N116_shear_0.pdf}
\includegraphics[height=1.2in]{N116_shear_2500.pdf}
\includegraphics[height=1.2in]{N116_shear_5000.pdf}
\includegraphics[height=1.2in]{N116_shear_7500.pdf}\\
  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets of all panels are generated from the results of continuum modeling simulations and the streamlines have a perfect agreement to the numerical results.
  }
    \label{figure9}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2.in]{N116_ext_0.pdf}
\includegraphics[height=2.in]{N116_ext_2000.pdf}\\
\includegraphics[height=2.in]{N116_ext_4000.pdf}
\includegraphics[height=2.in]{N116_ext_6500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets show the results produced from using continuum model that the streamlines have perfect agreements with the present results.
  }
    \label{figure8}
\end{figure}

@@

\section{\label{A2} Comparison between Continuum Model and the Proposed Model}

\begin{figure}
\centering
\includegraphics[height=1.2in]{N116_cont_a.pdf}
\includegraphics[height=1.2in]{N116_cont_b.pdf}
\includegraphics[height=1.2in]{N116_cont_c.pdf}
\includegraphics[height=1.2in]{N116_cont_d.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
  }
    \label{figureB}
\end{figure}

>>>>

Following the relaxation experiments of the Janus-vesicle, this section will focus on the behavior of vesicles 
under a number of flow types. To extract physical quantities of the target structure using the proposed model, the scaling laws and the dimensionless units are given as follows.
The length unit is scaled by the length of phospholipids $l=2.5$ nm and the force is scaled from the 
interfacial tension $\gamma=4.1$ pN nm$^{-1}$ from ~\cite{Ryham16}. We then be able to calculate the corresponding 
time scale $\tau = 0.38$ ns. With the same framework, \cite{Fu20} provides the bending rigidity 
$\kappa=8.51$ kT.

@@

\begin{figure}
\begin{center}
\hspace{-0.6cm}
\includegraphics[height=2in]{ReducedArea.pdf}
\hspace{0.6cm}
\includegraphics[height=2in]{DecayRate.eps}\\
\includegraphics[height=2in]{ArcLength.pdf}
\includegraphics[height=2in]{ExcLength.pdf}
\end{center} 
  \caption{(a) Total arc lengths of the midplanes over time in different shear rates; (b) From exponential fits in panel (a), we obtain the decay rate for a number of different shear rates;
  (c) Reduced area transitions over time. (d) Excess length of the midplanes.
A set of shear rates $\dot\gamma=\{0.002,0.0025,0.003,0.0035\}$ is used in simulations. 
A slower shear rate generates a faster convergence in the reduced area and smaller excess length. 
  }
    \label{figure4}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{parabolic.eps}
  \caption{Vesicle under a parabolic flow where the strength of the flow $v_{max}=8.0$ and the control parameter $w=10$. The configuration is the state when $t=10000$.
  }
    \label{figure6}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{N58_rupt_0.pdf}
\includegraphics[height=2in]{N58_rupt_200.pdf}
\\
\includegraphics[height=2in]{N58_rupt_400.pdf}
\includegraphics[height=2in]{N58_rupt_600.pdf}
  \caption{Membrane rupture occurs when the shear rate is beyond a certain threshold. Here the shear rate is $\dot\gamma = 0.1$. Starting with a circular shape (panel (a)), the vesicle is stretched by the background flow and multiple pores appear (panel (b)). (c)-(d) are the later states during the simulation.
  }
    \label{figure7}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{N116_shear_0.pdf}
\includegraphics[height=2in]{N116_shear_2500.pdf}\\
\includegraphics[height=2in]{N116_shear_5000.pdf}
\includegraphics[height=2in]{N116_shear_7500.pdf}
  \caption{Two vesicles under a shear flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets of all panels are generated from the results of continuum modeling simulations and the streamlines have a perfect agreement to the numerical results.
  }
    \label{figure9}
\end{figure}

@@

\begin{figure}
\centering
\includegraphics[height=2in]{N116_ext_0.pdf}
\includegraphics[height=2in]{N116_ext_2000.pdf}\\
\includegraphics[height=2in]{N116_ext_4000.pdf}
\includegraphics[height=2in]{N116_ext_6500.pdf}
  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; The initial configuration is shown in panel (a). The background color indicates the magnitude of fluid pressure. From dark red to dark blue, it represents the the pressure varies from high to low values. The color bar is valid for all panels. Streamlines are plotted in purple. The insets show the results produced from using continuum model that the streamlines have perfect agreements with the present results.
  }
    \label{figure8}
\end{figure}

@@

%\section{\label{A2} Comparison between Continuum Model and the Proposed Model}
%
%\begin{figure}
%\centering
%\includegraphics[height=1.2in]{N116_cont_a.pdf}
%\includegraphics[height=1.2in]{N116_cont_b.pdf}
%\includegraphics[height=1.2in]{N116_cont_c.pdf}
%\includegraphics[height=1.2in]{N116_cont_d.pdf}
%  \caption{Two vesicles under an extensional flow where the dimensioneless shear rate is $\dot\gamma=0.005$; Continuum modeling.....
%  }
%    \label{figureB}
%\end{figure}
